### 2020-06-12 2020-June11PresentationCAM.tex
Added files

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=red!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=red!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=red!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

% List your packages here

\usepackage[colorinlistoftodos]{todonotes}

\title[Progress Update]{Cleaning and Mapping Robotics Project}

% % A subtitle is optional and this may be deleted
% \subtitle{Product Proposal}

\author[B.~Lauer, J.~Kannagala]{Brian~Lauer \and Jaden~Kannagala \\\and
Advisor: Dr. Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[June~11,~2020]{Thursday, June~11,~2020}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

\subject{Mobile Robot Localization}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
% \AtBeginSubsection[]
% {
%   \begin{frame}<beamer>{Outline}
%     \tableofcontents[currentsection,currentsubsection]
%   \end{frame}
% }

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}{}
\begin{figure}
    \centering
    \includegraphics[scale=0.45]{figs/inkscape/mappingRobotArchitecture.eps}
    \caption{Diagram representing the working principle of the cleaning and mapping robot}
    \label{fig:my_label}
\end{figure}
\end{frame}

\section{Progress}

\begin{frame}{Progress}{}
    \begin{itemize}
        \item Created basic layout of the Android app for displaying the 2D room map in Android Studio
        \item Researched RPILidar S1 $360^\circ$ Laser Scanner
    \end{itemize}
\end{frame}

\begin{frame}{Progress}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.3]{figs/img/screenshot1}
        \caption{Screenshot of app with Discovery and Map tabs}
        \label{fig:my_label}
    \end{figure}
\end{frame}

\subsection{Further app details}
\begin{frame}{Progress}{Further app details}
    \begin{itemize}
        \item \texttt{TabLayout} View used for displaying tabs horizontally
        \item \texttt{Fragment} class used for both the discovery and map tabs
        \item To display items in a list, \texttt{ListView} is used for displaying a vertically-scrollable collection of views
        \item \texttt{ArrayAdapter} used for displaying Strings from an \texttt{ArrayList} in the \texttt{ListView}
        \item \texttt{AdapterView.setOnItemClickListener()} to register a callback when an item in the adapter view has been clicked
    \end{itemize}
\end{frame}

\subsection{Lidar}
\begin{frame}{Progress}{Lidar}
    \begin{figure}
        \centering
        \includegraphics[scale=1]{figs/img/15872-Slamtec_RPLIDAR_S1-01.jpg}
        \caption{RPILidar S1 $360^\circ$ TOF Laser Scanner, source: https://www.sparkfun.com/products/15872}
        \label{fig:my_label}
    \end{figure}
\end{frame}

\begin{frame}{Progress}{Lidar}
    \begin{itemize}
        \item Takes samples at a rate up to 9200 samples per second
        \item 40 meter range
        \item Built-in motor that rotates at 10 Hz (600 rpm)
        \item Data is transferred over serial connection 256000 bps
        \item Can be connected to a single board computer (Beaglebone Blue)
        \item Separate power interfaces for the scanner and motor (5V VCC)
    \end{itemize}
\end{frame}

\section{Plans}
\begin{frame}{Plans}{}
    \begin{itemize}
        \item Build custom adapter class for displaying network data of the discovered robot
        \item Write a server in Python for the Beaglebone to accept connections from mobile devices
        \item In the \texttt{DiscoveryFragment} class add code to automatically start discovering robots with TCP/IP client code
        \item Add a spinner in the UI while the app is waiting for robot connections
    \end{itemize}
\end{frame}
% You can reveal the parts of a slide one at a time
% with the \pause command:
%\begin{frame}{Second Slide Title}
%  \begin{itemize}
%  \item {
%    First item.
%    \pause % The slide will pause after showing the first item
%  }
  %\item {   
  %  Second item.
 % }
  % You can also specify when the content should appear
  % by using <n->:
 % \item<3-> {
 %   Third item.
 % }
%  \item<4-> {
%    Fourth item.
 % }
  % or you can use the \uncover command to reveal general
  % content (not just \items):
%  \item<5-> {
%    Fifth item. \uncover<6->{Extra text in the fifth item.}
%  }
%  \end{itemize}
%\end{frame}

%\section{Second Main Section}

%\subsection{Another Subsection}

%\begin{frame}{Blocks}
%\begin{block}{Block Title}
%You can also highlight sections of your %presentation in a block, with it's own %title
%\end{block}
%\begin{theorem}
%There are separate environments for %theorems, examples, definitions and proofs.
%\end{theorem}
%\begin{example}
%Here is an example of an example block.
%\end{example}
%\end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.
% \section*{Summary}

% \begin{frame}{Summary}
%   \begin{itemize}
%   \item
%     The \alert{first main message} of your talk in one or two lines.
%   \item
%     The \alert{second main message} of your talk in one or two lines.
%   \item
%     Perhaps a \alert{third message}, but not more than that.
%   \end{itemize}

%   \begin{itemize}
%   \item
%     Outlook
%     \begin{itemize}
%     \item
%       Something you haven't solved.
%     \item
%       Something else you haven't solved.
%     \end{itemize}
%   \end{itemize}
% \end{frame}

% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{References}

  \begin{thebibliography}{10}

  \setbeamertemplate{bibliography item}[online]

  \bibitem{android}
  Android Developer Docs
  \newblock \url{https://developer.android.com/}

  \bibitem{lidardatasheet}
  RPILidar S1 360 Datasheet
  \newblock \url{https://www.robotshop.com/media/files/content/r/rpk/pdf/rplidar-s1-360-laser-scanner-40-m-datasheet.pdf}
  \end{thebibliography}
\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-09-02 cleaningRobotDescription.tex
Added robot description

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amssymb}
\author{Brian Lauer}

\begin{document}

\begin{figure}
\centering
\includegraphics[scale=0.5]{figs/img/frontViewScreenshotB}
\caption{Current cleaning, disinfection, and mapping robot design}
\label{camRobot}
\end{figure}

Many different robots exist on the market for the purpose of UV disinfection from companies like UVD Robots. These robots typically employ sensors like ultrasonic sensors for ranging, LIDAR sensors or cameras for generation of a digital map of a room, and cliff sensors for recognition of drops or edges. One of the main features they employ is a UVC lamp that is capable of performing efficient elimination of many harmful microorganisms including bacteria and viruses within a room through DNA destruction and disruption. However, a limitation to these current robots on the market is the inability to shine UV light vertically: only horizontally with full 360$^\circ$ range of emission. The proposed robot design shown in Figure \ref{camRobot} will support emission of light horizontally as well as vertically by including two horizontally positioned lamps able to disinfect areas directly above the robot. Secondly, because UV light is deemed dangerous to humans and possibly other animals a disinfection sprayer will help to further reduce the concentration of harmful pathogens. In this way, full room disinfection can be accounted for in case any live animals are unable to be relocated during the disinfection period. During disinfection of a room with UVC light such as a hospital room, no humans or animals may be present. To provide a maximum turning radius and stability, the robot features a two-wheel differential drive design with two additional points of contact via two caster wheels. For creation of a digital map, a LIDAR sensor is present in the center of the robot which will relay serial data to the robot's central computer, a Beaglebone single board computer with the SLAM (Simultaneous Localization and Mapping) algorithm.

Another feature that the proposed robot will boast is the presence of a vacuuming mechanism capable of removing dust particles or debris from floor surfaces. In this way, a room can be thoroughly cleaned with little to no human intervention which is in favor due to the current health crisis. This robot will be able to effectively combine the features of the robot designs by iRobot and UVD robots. Another feature that this robot will propose to implement is the integration of a mobile application capable of wireless communication with the onboard computer of the robot to direct the robot to perform various actions like directing the robot to a specific room or area of a home or building. Secondly, a real time 2D map of the room will be visible to allow owners to view the current progress of the cleaning and disinfection process. Lastly, 14 ultrasonic sensors will be present around the circumference of the robot chassis to perform additional ranging and obstacle avoidance.
\end{document}

### 2020-12-23 cleaningRobotDescription.tex

@@
 \usepackage{amssymb}
-\author{Brian Lauer}
+\usepackage{fullpage}
+\title{Cleaning, Disinfection, and Mapping Robot}
+\author{Brian Lauer\and Suruz Miah}
 
 \begin{document}
+\maketitle
 
-\begin{figure}
+Nowadays, many different robots are available on the market for the purpose of
+ultraviolet (UV) disinfection from companies like UVD
+Robots\footnote{http://www.uvd-robots.com/}. These robots typically employ
+sensors, such as ultrasonic sensors for ranging, LIDAR sensors or cameras for
+creating a map of a room, and cliff sensors for recognition of
+drops or edges. One of the main features of these robots is to utilize UVC lamp that is
+capable of performing efficient elimination of many harmful microorganisms
+including bacteria and viruses within a room through DNA destruction and
+disruption. However, a limitation to these current robots on the market is the
+inability to shine UV light vertically: only horizontally with full 360$^\circ$
+range of emission. The proposed robot design shown in Figure~\ref{camRobot} will
+support emission of light horizontally as well as vertically by including two
+horizontally positioned lamps able to disinfect areas directly above the
+robot. %
+%
+\begin{figure}[htbp]
   \centering
@@
 \end{figure}
+%
+Secondly, because UV light is deemed dangerous to humans and possibly other
+animals a disinfection sprayer will help to further reduce the concentration of
+harmful pathogens. In this way, full room disinfection can be accounted for in
+case any live animals are unable to be relocated during the disinfection period.
+During disinfection of a room with UVC light such as a hospital room, no humans
+or animals may be present. To provide a maximum turning radius and stability,
+the robot features a two-wheel differential drive design with two additional
+points of contact via two caster wheels. To generate a digital map, a LIDAR
+sensor is present in the center of the robot which will relay serial data to the
+robot's central computer, a Beaglebone single board computer with the SLAM
+(Simultaneous Localization and Mapping) algorithm.
 
-Many different robots exist on the market for the purpose of UV disinfection from companies like UVD Robots.
-These robots typically employ sensors like ultrasonic sensors for ranging, LIDAR sensors or cameras for generation of a digital map of a room, and cliff sensors for recognition of drops or edges.
-One of the main features they employ is a UVC lamp that is capable of performing efficient elimination of many harmful microorganisms including bacteria and viruses within a room through DNA destruction and disruption.
-However, a limitation to these current robots on the market is the inability to shine UV light vertically: only horizontally with full 360$^\circ$ range of emission.
-The proposed robot design shown in Figure \ref{camRobot} will support emission of light horizontally as well as vertically by including two horizontally positioned lamps able to disinfect areas directly above the robot.
-Secondly, because UV light is deemed dangerous to humans and possibly other animals a disinfection sprayer will help to further reduce the concentration of harmful pathogens.
-In this way, full room disinfection can be accounted for in case any live animals are unable to be relocated during the disinfection period.
-During disinfection of a room with UVC light such as a hospital room, no humans or animals may be present.
-To provide a maximum turning radius and stability, the robot features a two-wheel differential drive design with two additional points of contact via two caster wheels.
-For creation of a digital map, a LIDAR sensor is present in the center of the robot which will relay serial data to the robot's central computer, a Beaglebone single board computer with the SLAM (Simultaneous Localization and Mapping) algorithm.
+Another feature that the proposed robot will boast is the presence of a
+vacuuming mechanism capable of removing dust particles or debris from floor
+surfaces. In this way, a room can be thoroughly cleaned with little to no human
+intervention which is in favor due to the current health crisis. This robot will
+be able to effectively combine the features of the robot designs by iRobot and
+UVD robots. Another feature that this robot will propose to implement is the
+integration of a mobile application capable of wireless communication with the
+onboard computer of the robot to direct the robot to perform various actions
+like directing the robot to a specific room or area of a home or building.
+Secondly, a real time 2D map of the room will be visible to allow owners to view
+the current progress of the cleaning and disinfection process. Lastly, 14
+ultrasonic sensors will be present around the circumference of the robot chassis
+to perform additional ranging and obstacle avoidance.
+\end{document}
 
-Another feature that the proposed robot will boast is the presence of a vacuuming mechanism capable of removing dust particles or debris from floor surfaces.
-In this way, a room can be thoroughly cleaned with little to no human intervention which is in favor due to the current health crisis.
-This robot will be able to effectively combine the features of the robot designs by iRobot and UVD robots.
-Another feature that this robot will propose to implement is the integration of a mobile application capable of wireless communication with the onboard computer of the robot to direct the robot to perform various actions like directing the robot to a specific room or area of a home or building.
-Secondly, a real time 2D map of the room will be visible to allow owners to view the current progress of the cleaning and disinfection process.
-Lastly, 14 ultrasonic sensors will be present around the circumference of the robot chassis to perform additional ranging and obstacle avoidance.
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2021-01-06 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex
Created paperFLAIRS34 folder and the paper template

\def\year{2021}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS

\usepackage{amssymb,amsmath,bm}
\usepackage{graphics,adjustbox}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}

\usepackage[figuresright]{rotating}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[english,algo2e,algoruled,vlined,linesnumbered]{algorithm2e}   % package for algorithm
\usepackage{enumerate}

\usepackage{easyReview}
\newtheorem{assumption}{Assumption}

\DeclareMathOperator*{\argmin}{arg min}

\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
 \pdfinfo{
/Title (Smart Sanitizing Indoor Mobile Robot: Design and Development)
/Author (Brian Lauer, Nicoulas Shepard, Fazel Keshtkar, and Md Suruz Miah)
} %Leave this	
% /Title ()
% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
% Leave the space between \Title and the beginning parenthesis alone
% /Author ()
% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case. 
% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands, 
% remove them.

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{caption} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \natbib} -- This package is specifically forbidden -- use the following workaround:
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai20.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\setlength\titlebox{2.5in} % If your paper contains an overfull \vbox too high warning at the beginning of the document, use this
% command to correct it. You may not alter the value below 2.5 in
\title{Smart Sanitizing Indoor Mobile Robot: Design and Development}
%Your title must be in mixed case, not sentence case. 
% That means all verbs (including short verbs like be, is, using,and go), 
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\author{~%
Brian Lauer\textsuperscript{\rm 1}, Nicoulas Shepard\textsuperscript{\rm 1},
Fazel Keshtkar\textsuperscript{\rm 2}, and Md Suruz Miah\textsuperscript{\rm 1}
\\  
\textsuperscript{\rm 1}Electrical and Computer Engineering, Bradley University, Peoria, IL, USA; emails:~\{blauer,nshepard\}@mail.bradley.edu,~smiah@bradley.edu\\
\textsuperscript{\rm 2}Computer Science, Math. and Science, St John's University, Queens, NY, USA; email:~keshtkaf@stjohns.edu
}
 \begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\section{Existing Sanitizing Robots} 
\label{sec:Literature}

\section{System Architecture}
\label{sec:SystemArchitecture}

\todo[inline]{Discuss two different architecture that we propose}

\begin{figure}[htpb]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[scale=0.25]{../figs/img/frontViewScreenshotB}
    \caption{Overall design of the proposed smart sanitizing robot.}
    \label{fig:frontViewScreenshotB}
  \end{subfigure}
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \includegraphics[scale=0.1]{../figs/img/v2BodyDesign}
    \caption{Body design}
  \end{subfigure}
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \includegraphics[scale=0.1]{../figs/img/v2UVLamp}
    \subcaption{UV lamp model}
  \end{subfigure}
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \includegraphics[scale=0.1]{../figs/img/v2UVLampConveyor}
    \subcaption{UV lamp conveyor}
  \end{subfigure}
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \includegraphics[scale=0.1]{../figs/img/v2SprayerMount}
    \subcaption{Disinfectant sprayer mount}
  \end{subfigure}
  \caption{Design of Proposed Sanitizing Robots.}
  \label{fig:ArchitecturesOfSanitizingRobot}
\end{figure}

\subsection{Features}
\label{sec:Features}

\subsection{Operating Principle}
\label{sec:OperatingPrinciple}

\section{Detailed Design}
\label{sec:DetailedDesign}

\section{Real-Time Computer Experiment}
\label{sec:RealTimeComputerExperiment}

\section{Conclusion} \label{sec:conclusion}

% \bibliographystyle{aaai}
% \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-01-14 coppeliaSim/testRobotDemo.m
Added scenes and code

@@ -1,0 +1,39 @@
+clear all;
+close all;
+clc;
+
+addpath('libCoppelia/');
+
+disp('Program started');
+vrep = remApi('remoteApi');
+vrep.simxFinish(-1);
+clientID = vrep.simxStart('127.0.0.1',19999,true,true,5000,5);
+if(clientID> -1)
+    disp('Connected to the remote API server');
+    vrep.simxAddStatusbarMessage(clientID,'Hello Coppelia Sim!',vrep.simx_opmode_oneshot);
+else
+    disp('Failed connecting to the remote API server');
+    return;
+end
+
+[rtn, robot_id(1,1)] = vrep.simxGetObjectHandle(clientID, 'main_body',...
+vrep.simx_opmode_oneshot_wait);
+if(rtn ~= vrep.simx_return_ok)
+    disp('Get test robot handle failed');
+end
+
+[rtn, robot_id(1,2)] = vrep.simxGetObjectHandle(clientID,'right_motor',...
+    vrep.simx_opmode_oneshot_wait);
+if(rtn~=vrep.simx_return_ok)
+    disp('Get front right motor handle failed');
+end
+
+[rtn,robot_id(1,3)] = vrep.simxGetObjectHandle(clientID,'left_motor',...
+    vrep.simx_opmode_oneshot_wait);
+if(rtn~=vrep.simx_return_ok)
+    disp('Get front left motor handle failed');
+end
+
+pause(1);
+vrep.simxSetJointTargetVelocity(clientID,robot_id(1,2),0.2,vrep.simx_opmode_oneshot);
+vrep.simxSetJointTargetVelocity(clientID,robot_id(1,3),-0.2,vrep.simx_opmode_oneshot);

### 2021-01-15 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex
Updated paper with literature review (in process)

@@
 \section{Existing Sanitizing Robots} 
+\section{Existing Sanitizing Robots} 
 \label{sec:Literature}
+There are many ways of transmitting infections disease, and studies have shown that the greatest cause of contact surface such as: remote control, door handles or cabinets, a button to call for help, etc.
+UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria.
+UV-C disinfection robot provides an economical and effective measure in limiting the spread of bacteria.
+When bacteria are exposed to UV-C light of their DNA absorbs light energy and causes cell damage that prevents new infecting others.
+The robot is controlled by the medical staff and the time for which disinfect a room is 10–15 min depending on the size of the room.
+
+\subsubsection{Service Robots for Disinfection}
+In their paper, \cite{Begic2018} investigated the use of of the service robots in medicine with an emphasis on service robots for disinfection in medical institutions.
+They found that  disinfectant service robots are fast and effective in medical institutions.
+Most imprtant;y, they found that use of the service robots reduces the risk of infection, cost of traditional cleaning and disinfection, and most importantly acquires confidence and security in medical facilities.
+In their paper, they investigated following service robots:
+\begin{itemize}
+	\item \textbf{Robot 'IRIS 3200 m'}
+	One of the UV light robot is \verb|IRIS 3200 m|, which  is the most powerful system for disinfecting UV light in the world.
+This robot   UVC generate UVC  up to 20 times the UVC output tested xenon pulse system and three times the power of other constant light competitors.
+	This robot uses  patented SmartDosage, together with the patented box Balance and PowerBoost technology allow 'iris 320m' UV lighting system of disinfection for automatically measuring conditions the room environment, such as the size of the room, temperature and humidity in order to determine in real time the appropriate dose, time, number and power of the lamp is required for complete disinfection of all while providing maximum power permitted in the United States for the production of germicidal UVC energy.
+
+	IRIS 3200 m is ideal for the hospital which require the maximum disinfection least amount of time.
+Benefits 'Iris 3200 m' UV light disinfection system are: Faster treatment room, Higher productivity, More effective treatments, Highly pathogenic kills prices, Whole-room treatments, One placement, One treatment
+
+	\item "Xenex Germ-Zapping" Robots
+	High intensity ultraviolet light is produced by xenon flash lamps across the entire disinfecting spectrum known as UV-C.
+This UV-C energy passes through the cell walls of bacteria, viruses and bacterial spores.
+The DNA, RNA and proteins inside the microorganism absorb this intense UV-C energy.
+Xenex Full Spectrum UV-C provides four mechanisms of damage against pathogens.
+	The primary types of cellular damage caused by Pulsed Xenon UV are photohydration (pulling water molecules into the DNA that prevents transcription), photosplitting (breaking the backbone of the DNA), and photodimerization (improper fusing of DNA bases), all of which prevent cell replication.
+\end{itemize}
+
+\subsubsection{Wall-Following Behavior for a Disinfection Robot Using Type 1 and Type 2 Fuzzy Logic Systems}
+% https://pubmed.ncbi.nlm.nih.gov/32784888/
+\cite{Muthugaletal2020} 
+Robot-aided solutions are demanded to disinfect possibly contaminated surfaces to reduce the spread of infectious diseases.
+A wall disinfection robot should be capable of following a given wall while maintaining a specified distance from the wall.
+The ability to maintain the specified distance from the wall is crucial for the effective sterilization of the wall surface since the intensity of the disinfectant agent applied on the wall depends on the distance.
+The disinfectant agent can be either a sprayable liquid, a gas, or ultraviolet light directed at the wall.
+Therefore, this paper proposed a novel method to establish the wall-following behavior for a disinfection robot.
+The proposed method was designed in such a way that it enables a robot to follow a wall of an unknown environment by online path planning based on the range sensor information.
+Fuzzy logic was used for establishing the wall-following behavior based on the range sensor inputs.
+A Type 1 Fuzzy Logic System (T1-FLS) and an Interval Type 2 Fuzzy Logic System (IT2-FLS) were proposed in this regard.
+The FLSs were designed in such a way that they were generalized from the lateral distance to be maintained from a wall.
+Moreover, users can alter the lateral distance per the requirements without performing any redesign work of the system.
+The FLSs take the information perceived from range sensors as inputs and determine the linear velocity and the angular velocity of the robot required to follow a wall successfully.
+Simulations were conducted to evaluate the characteristics and performance of the proposed FLSs.
+Heterogeneous test cases that consisted of typical wall arrangements were considered in the simulation.
+According to the simulation results, both proposed FLSs (i.e., T1-FLS and IT2-FLS) were capable of adequately following walls as expected for a wall disinfection robot.
+A superior performance could be observed from the IT2-FLS compared to that of the T1-FLS, and this performance difference was large and statistically significant.
+The real-world applicability of the proposed method was verified from the simulations, and it is expected that real-world trials will be conducted in the next phase of the work.
+
+\subsubsection{UVC disinfection robot}
+%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7556603/
+
+\cite{Guettari2020} The aim of the present work is to contribute in the fight against the spread of Covid-19, a novel human coronavirus, in hospitals, public transport, airlines, and any enclosed areas.
+They have adopted the physical disinfection method by using UVC light as agent.
+The UVC devices are studied and classified according their disinfectant units, complementary devices, combined disinfection agents, mobilities, and order types.
+Their finding shows that a mobile robot is the most efficient device to inactivate microorganisms, so they have developed a robot called 'i-Robot UVC'.
+The robot is equipped with eight UVC lamps around a central column and two lamps on the top.
+i-Robot UVC can be controlled manually or run automatically; the robot is designed especially for all areas of hospital and any enclosed space to inactivate microorganisms.
+The construction of the robot involved: (1) the structural building, (2) the electronic assembling, and (3) the programming of the microcontroller and the mobile application.
+The structure was made by attaching to a central column two horizontal crows to immobilize eight UVC lamps.
+Two other lamps are mounted on top of the robot; the system of lamps can cover the space around the device.
+The power supply of the device is done with a direct voltage of 24 V which supplies energy to the UVC lamps and supplies the Arduino board and the rest of the electronic circuit.
+
+Some features of i-Robot UVC:   disinfectant time is estimation based on space,  the temperature, and the humidity rate; uses ultrasound sensor to detect and measure the distance; Using infrared sensors  to detect motion;  robot operates when people are not around and turns off the UVC lamps otherwise; using  to LiDAR sensor, the robot scans the environment and creates a digital map; this permits to optimize intervention.
+An operator equipped by protective suit controls the robot operation from a dashboard thanks to integrated cameras.
 
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusion}
+\label{sec:conclusion}
 
-% \bibliographystyle{aaai}
-% \bibliography{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
+ \bibliographystyle{aaai}
+ \bibliography{bib/flairs34}
+ %{bib/refsSuruzWeb,bib/refsMultiAgent,bib/refsRoboticsJournals,bib/refsRoboticsConferences,bib/refsGenericControl,bib/refsBooksTRTheses,bib/refsReinforcementLearningADP,bib/refsRL-Keshtkar}
 

### 2021-01-15 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex
Paper: Introduction section in process (Dr. Miah)

--- 2021-01-06 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex
@@
 % command to correct it. You may not alter the value below 2.5 in
-\title{Smart Sanitizing Indoor Mobile Robot: Design and Development}
+\title{Smart Sanitizing Mobile Robot using Ultra-violet Sterilization
+  Technology: A Prototype}
 %Your title must be in mixed case, not sentence case. 
@@
 \begin{abstract}
+
+  In this paper, we propose a design of a smart sanitizing wheeled mobile robot
+  using ultra-violet (UV) sterilization technology. The current design of the
+  robot includes exteroceptive sensors, such as sonars, a lidar, a radio-frequency
+  transceiver, and a camera. A circular-shaped UV [wavelength is in the range of
+  $200~\nano\meter$--$280~\nano\meter$ (C band)] LED light is mounted on top
+  of the robot for the purpose of sterilization in sanitizing complex indoor
+  environments. The proposed robot under development is expected to sanitize  
+  complex environments smartly in the sense that the UV LED is mounted with an actuator so that the robot can
+  easily adapt the height of the UV LED based on the map of the operating
+  environment. The performance of the robot is
+  initially tested using the commercial robot simulator in an indoor environment
+  with various complexities.
+
 \end{abstract}
@@
 
-\section{Existing Sanitizing Robots} 
-\label{sec:Literature}
+The design and development of a class of mobile robots in sterilizing indoor
+environments, hospitals, offices, and other indoor spaces, for example, have
+received a special attention in recent years, especially due to Coronavirus
+diseases - 2019 (COVID-19)\todo[inline]{Reference}. Recently, a class of mobile robots has been
+developed to sterilize indoor spaces using UV-C sterilization
+technology~\todo[inline]{Reference}. Most of the mobile robots developed so far in
+sanitizing indoor environments either rely on fixed-mount UV-tube or sprayers to
+disinfect areas much like a conventional cleaning robot. It is worth noting
+that, not many sanitizing robots use UV lights to disinfect robot based on the
+map of the indoor operating environment. In this paper, we develop a prototype
+of a modular and cost-effective mobile robot, where robot has the ability to
+smartly decide on the indoor space to  be sterilize based on the map. The map of
+the environment is created using sensor fusion technology much like what
+conventional autonomous robots do using range and vision sensors.
+
+\todo[inline]{Talk about some existing sanitizing robots available in the market}
 

### 2021-01-15 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex

--- 2021-01-15 paperFLAIRS34-LatexCode/paperFLAIRS2021-V1.tex
@@
 
+-The design and development of a class of mobile robots in sterilizing indoor
+-environments, hospitals, offices, and other indoor spaces, for example, have
+-received a special attention in recent years, especially due to Coronavirus
+-diseases - 2019 (COVID-19)\todo[inline]{Reference}. Recently, a class of mobile robots has been
+-developed to sterilize indoor spaces using UV-C sterilization
+-technology~\todo[inline]{Reference}. Most of the mobile robots developed so far in
+-sanitizing indoor environments either rely on fixed-mount UV-tube or sprayers to
+-disinfect areas much like a conventional cleaning robot. It is worth noting
+-that, not many sanitizing robots use UV lights to disinfect robot based on the
+-map of the indoor operating environment. In this paper, we develop a prototype
+-of a modular and cost-effective mobile robot, where robot has the ability to
+-smartly decide on the indoor space to  be sterilize based on the map. The map of
+-the environment is created using sensor fusion technology much like what
+-conventional autonomous robots do using range and vision sensors.
 \section{Existing Sanitizing Robots} 
